Governing through patronage: the bargain for education in decentralized Brazil

### 2020-11-16 paper/paper.tex
commit changes to saeb exam scores
fix descriptive stats for teacher

Teachers and school principals are responsible for providing all educational services at the local level. As of 2016, in the municipal education system there were 3.7 million teachers distributed across the national territory, as well as 148 thousand school principals. TableA majority of teachers are hired with a permanent contract (\emph{estatutário}) Over the past decade, there has been an increasing

>>>>

Teachers and school principals are responsible for providing all educational services at the local level. As of 2016, in the municipal education system there were 3.7 million teachers distributed across the national territory, as well as 148 thousand school principals. A majority of teachers are hired with a permanent contract (\emph{estatutário}) Over the past decade, there has been an increasing

\begin{table}[t]
    \input{results/descriptive_teacher}
    \caption{\textbf{Summary statistics for municipal teachers.} All statistics take as reference year 2017 as reference.}
\end{table}

### 2020-11-16 paper/results/descriptive_teacher.tex
fix descriptive stats for teacher

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mon, Nov 09, 2020 - 12:09:20 PM
\begin{tabular}{@{\extracolsep{5pt}}lccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} \\ 
\hline \\[-1.8ex] 
Number of teachers per school & 72,642 & 4.108 & 4.335 & 1 & 86 \\ 
Number of classes per school & 72,642 & 4.126 & 4.417 & 1 & 173 \\ 
Proportion of teachers w/ higher education & 72,642 & 0.729 & 0.377 & 0 & 1 \\ 
Average age & 72,642 & 0.811 & 0.283 & 0.000 & 1.000 \\ 
Average nunber of classes per teacher & 72,642 & 40.008 & 7.251 & 16.000 & 75.000 \\ 
mean\_n\_class\_per\_teacher & 72,642 & 1.025 & 0.248 & 0 & 7 \\ 
\hline \\[-1.8ex] 
\end{tabular}

>>>>

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mon, Nov 16, 2020 - 10:49:28 AM
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Statistic & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} \\ 
\hline \\[-1.8ex] 
Number of teachers per school & 4.108 & 4.335 & 1 & 86 \\ 
Number of classes per school & 4.126 & 4.417 & 1 & 173 \\ 
Proportion of teachers w/ higher education & 0.729 & 0.377 & 0 & 1 \\ 
Average age & 0.811 & 0.283 & 0.000 & 1.000 \\ 
Average number of classes per teacher & 40.008 & 7.251 & 16.000 & 75.000 \\ 
mean\_n\_class\_per\_teacher & 1.025 & 0.248 & 0 & 7 \\ 
\hline \\[-1.8ex] 
\end{tabular}
